A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-05-15 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.Rmd
Updated link to repository and acknowledgments before production.

Please note that this paper is prepared as a reproducible research document. The source `R` markdown document, as well as all data and code needed to reproduce/review/extend the analysis can be obtained from a public repository\footnote{\url{https://drive.google.com/drive/u/1/folders/1d_40N_QXo2Fl14r3T3CHs84IED-B1rV_}}.

@@

Add acknowledgments as appropriate in final draft.

The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `aemet` [@Rodriguez2018aemet], `ggthemes` [@Arnold2019], `gridExtra` [@Auguie2017gridextra], `kableExtra` [@Zhu2019], `knitr` [@Xie2014; @Xie2015], `lubridate` [@Grolemund2011dates], `plm` [@Millo2017robust], `rticles` [@Allaire2020], `sf` [@Pebesma2018], `spdep` [@Bivand2013], spsur [@Angulo2020spsur] `tidyverse` [@Wickham2019], `units` [@Pebesma2016].

>>>>

Please note that this paper is prepared as a reproducible research document. The source `R` markdown document, as well as all data and code needed to reproduce/review/extend the analysis can be obtained from a public repository\footnote{\url{https://github.com/paezha/covid19-environmental-correlates}}.

@@

Fernando A. López is supported by the program Groups of Excellence of the Region of Murcia, Fundación Séneca, Science and Technology Agency of the region of Murcia project 19884/GERM/15. Tatiane Menezes, Renata Cavalcanti, and Maira Galdino da Rocha Pitta are supported by Brazil's Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) and Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (Fundação Capes). Antonio Páez is not supported by Canada's Research Councils. The following `R` packages were used in the course of this investigation and the authors wish to acknowledge their developers: `aemet` [@Rodriguez2018aemet], `ggthemes` [@Arnold2019], `gridExtra` [@Auguie2017gridextra], `kableExtra` [@Zhu2019], `knitr` [@Xie2014; @Xie2015], `lubridate` [@Grolemund2011dates], `plm` [@Millo2017robust], `rticles` [@Allaire2020], `sf` [@Pebesma2018], `spdep` [@Bivand2013], spsur [@Angulo2020spsur] `tidyverse` [@Wickham2019], `units` [@Pebesma2016].

### 2020-05-15 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.tex
Updated link to repository and acknowledgments before production.

Please note that this paper is prepared as a reproducible research
document. The source \texttt{R} markdown document, as well as all data
and code needed to reproduce/review/extend the analysis can be obtained
from a public
repository\footnote{\url{https://drive.google.com/drive/u/1/folders/1d_40N_QXo2Fl14r3T3CHs84IED-B1rV_}}.

@@

Add acknowledgments as appropriate in final draft.

The following \texttt{R} packages were used in the course of this
investigation and the authors wish to acknowledge their developers:
\texttt{aemet} (Rodriguez-Sanchez et al., 2018), \texttt{ggthemes}
(Arnold, 2019), \texttt{gridExtra} (Auguie, 2017), \texttt{kableExtra}
(Zhu, 2019), \texttt{knitr} (Xie, 2015, 2014), \texttt{lubridate}
(Grolemund and Wickham, 2011), \texttt{plm} (Millo, 2017),
\texttt{rticles} (Allaire et al., 2020), \texttt{sf} (Pebesma, 2018),
\texttt{spdep} (Bivand et al., 2013), spsur (Angulo et al., 2020)
\texttt{tidyverse} (Wickham et al., 2019), \texttt{units} (Pebesma et
al., 2016).

>>>>

Please note that this paper is prepared as a reproducible research
document. The source \texttt{R} markdown document, as well as all data
and code needed to reproduce/review/extend the analysis can be obtained
from a public
repository\footnote{\url{https://github.com/paezha/covid19-environmental-correlates}}.

@@

Fernando A. López is supported by the program Groups of Excellence of
the Region of Murcia, Fundación Séneca, Science and Technology Agency of
the region of Murcia project 19884/GERM/15. Tatiane Menezes, Renata
Cavalcanti, and Maira Galdino da Rocha Pitta are supported by Brazil's
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) and
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (Fundação
Capes). Antonio Páez is not supported by Canada's Research Councils. The
following \texttt{R} packages were used in the course of this
investigation and the authors wish to acknowledge their developers:
\texttt{aemet} (Rodriguez-Sanchez et al., 2018), \texttt{ggthemes}
(Arnold, 2019), \texttt{gridExtra} (Auguie, 2017), \texttt{kableExtra}
(Zhu, 2019), \texttt{knitr} (Xie, 2015, 2014), \texttt{lubridate}
(Grolemund and Wickham, 2011), \texttt{plm} (Millo, 2017),
\texttt{rticles} (Allaire et al., 2020), \texttt{sf} (Pebesma, 2018),
\texttt{spdep} (Bivand et al., 2013), spsur (Angulo et al., 2020)
\texttt{tidyverse} (Wickham et al., 2019), \texttt{units} (Pebesma et
al., 2016).
